Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-26 paper.tex
Working on results section

\subsubsection{Time (TODO: HP/MARKM)}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_cont_cdf}
    \caption{CDF of time to touch a page while swapping for continuous
    benchmark. Notice that the y-axis scale is from 99.75\% to 100\%.}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_rand_cdf}
    \caption{CDF of time to touch a page while swapping for random benchmark.
    Notice that the y-axis scale is from 93\% to 100\%.}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_time_cont}
    \caption{Time to touch a page while swapping for continuous benchmark.
    Notice that the y-scale is logarithmic.}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_time_rand}
    \caption{Time to touch a page while swapping for random benchmark.}
\end{figure}

This experiment is designed to measure the impact of swapping on memory
operation latency.

>>>>

\subsubsection{Time}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_cont_cdf}
    \caption{CDF of time to touch a page while swapping for continuous
    benchmark. Notice that the y-axis scale is from 99.75\% to 100\%.
    \label{fig:swap_time_cont_cdf}}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_rand_cdf}
    \caption{CDF of time to touch a page while swapping for random benchmark.
    Notice that the y-axis scale is from 93\% to 100\%.\label{fig:swap_time_rand_cdf}}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_time_cont}
    \caption{Time to touch a page while swapping for continuous benchmark.
    Notice that the y-scale is logarithmic.\label{fig:swap_time_cont}}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_time_rand}
    \caption{Time to touch a page while swapping for random benchmark.\label{fig:swap_time_rand}}
\end{figure}

This experiment is designed to measure the impact of swapping on memory
operation latency. Figure \ref{fig:swap_time_cont} and Figure
\ref{fig:swap_time_rand} show the results.

The overall behavior is as expected. In the random benchmark, as before, all
memory is exhausted quickly, and the benchmark induces swapping soon after the
benchmark begins. Many memory accesses thus take milliseconds to complete
because they require paging in or out, which in turn depends on disk latency.
Even so, the majority of benchmark run time comes from a minority of accesses.
Figure \ref{fig:swap_time_rand_cdf} shows that as much as 95\% of memory
accesses occur on the micro-second scale. Of the remaining 5\%, almost all
accesses complete in less than 20ms. Moreover, notice that the size of the
swapfile makes very little difference in this workload because the disk has to
do random seeks regardless of swapfile size.

The continuous benchmark has more surprising results. Notice that Figure
\ref{fig:swap_time_cont} has a logarithmic y-scale. The system only begins to
swap after about 4M operations, as before. Unlike the random benchmark, we see a
number of operations that take hundreds of milliseconds. Figure
\ref{fig:swap_time_cont_cdf} shows that these only form a fraction of a percent
of all accesses done after swapping starts. However, Figure (TODO: figure) shows
that these few accesses form a majority of run time; they impact performance
significantly. (TODO: why do they happen).

We also find that in the continuous benchmark, a larger swapfile actually has
slight more of these slow memory accesses. We believe this has to do with the
fact that the large swapfile has less disk locality, and so causes more disk
seeks when paging out.

~\\ \textbf{Conclusions} TODO

Large swapfiles should be created with disk locality or on SSDs.
